Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-23 doc/JFLA2022/paper.tex
fix more typos

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the the graphical representation of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form. For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

Let $\alpha<\epsilon_0$ be an ordinal.
Using the \texttt{coq-equations} plug-in~\cite{sozeau:hal-01671777}, we define the function which returns the number of steps of the battle starting with $\alpha$ at step $i$ for  any $i\in\mathbb{N}$.
We prove that this number is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Wainer Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}, defined by transfinite recursion in Fig.~\ref{fig:Hprime}.
From this result, we infer that the considered function is not primitive recursive in general (for $\alpha\geq\omega^\omega$).

\begin{figure}[h]
 \noindent
 For any $i\in\mathbb{N}$,
   \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$.
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(i)$.
\end{itemize}
\vspace{4pt}
\inputsnippets{HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}

>>>>

 \begin{itemize}
   \item The game starts at an initial step $i\in\mathbb{N}$ (not necessarily $0$).
   \item  The hydra is always the  representation as a tree of some ordinal strictly below $\epsilon_0$ in Cantor normal
     form. For instance, Fig~\ref{fig:round} shows the hydras respectively associated with  $\omega^{\omega^2+1}$ and $\omega^{\omega^2}\times 3$.

@@

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from~\cite{KS81}.

We also study the number of steps of a battle:
Let $\alpha<\epsilon_0$ be an ordinal.
Using the \texttt{coq-equations} plug-in~\cite{sozeau:hal-01671777}, we define the function which returns the number of steps of the battle starting with $\alpha$ at step $i$, for  any $i$ in $\mathbb{N}$.
We prove that this number is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Wainer Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}, defined by transfinite recursion in Fig.~\ref{fig:Hprime}.
From this result, we infer that the considered function is not primitive recursive in general (for $\alpha\geq\omega^\omega$).

\begin{figure}[h]
 \noindent
 For any $\alpha$ in $[0,\epsilon_0)$ and any $i$ in $\mathbb{N}$,
   \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$.
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(i)$.
\end{itemize}
\vspace{4pt}
\inputsnippets{HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}
